Reanalysis Step 3: Propensity Score Analysis with Twang

### 2025-08-17 reanalysis-3-propensity_scores.qmd
twang

  # Extract propensity scores - twang stores them in the ps slot
  ps_scores <- tryCatch({
    if (!is.null(twang_model$ps)) {
      # ps can be a matrix (multiple stop methods) or vector (single stop method)
      if (is.matrix(twang_model$ps) || is.data.frame(twang_model$ps)) {
        twang_model$ps[, 1]  # Get first column
      } else {
        twang_model$ps  # Already a vector
      }
    } else {
      # Shouldn't happen but fallback to weights
      weights
    }
  }, error = function(e) {
    weights  # Use weights as fallback
  })

  # Create simple histograms
  par(mfrow = c(1, 2))

  # Control group
  hist(ps_scores[!treated], 
       main = paste("Control - Imputation", i),
       xlab = "Propensity Score",
       col = "lightblue",
       breaks = 20)

  # Treated group  
  hist(ps_scores[treated],
       main = paste("Treated - Imputation", i),
       xlab = "Propensity Score", 
       col = "lightcoral",
       breaks = 20)

  par(mfrow = c(1, 1))
}
```

>>>>

  # For twang models, propensity scores may not be directly accessible
  # We can use the weights to show distribution instead
  # Since weights = 1/PS for treated and 1/(1-PS) for control in ATT weighting

  # Create histograms of weights instead of propensity scores
  par(mfrow = c(1, 2))

  # Control group weights
  hist(weights[!treated], 
       main = paste("Weights: Control - Imputation", i),
       xlab = "Weight",
       col = "lightblue",
       breaks = 20)

  # Treated group weights (should all be 1 for ATT)
  hist(weights[treated],
       main = paste("Weights: Treated - Imputation", i),
       xlab = "Weight", 
       col = "lightcoral",
       breaks = 20)

  par(mfrow = c(1, 1))

  # Also show weight summary
  message("  Weight summary:")
  message("    Control: mean = ", round(mean(weights[!treated]), 3), 
          ", max = ", round(max(weights[!treated]), 3))
  message("    Treated: mean = ", round(mean(weights[treated]), 3),
          " (should be 1.0 for ATT)")
}
```
